To Do

### 2019-01-08 To_Do.Rmd
Corrected Scheper name

[ ] Bartomeus PNAS estimates (Nacho) 
[ ] Sheper PNAS estimates (MA)
[ ] UE red list (via @ropensci; MA)
[ ] SPAIN trends (MA: species with Brain size; Nacho or Cristina: trends)

@@

[ ] LHT Bartomeus PNAS + Shepper PNAS + Traitbase (Var) Nacho
[ ] Brain: MA (Spain + ND + US Ferran + US Parker): MA
[ ] Habitats USA: MA; Others ¿?: MA
[ ] Exotic use ¿? (Nacho)
[ ] Innovation (some in MA bbdd)
[ ] Invasive species in US. (Nacho)

>>>>

[ ] Bartomeus PNAS estimates (Nacho) 
[ ] Scheper PNAS estimates (MA)
[ ] UE red list (via @ropensci; MA)
[X] SPAIN trends (MA: species with Brain size) 
[ ] Trends: Nacho or Cristina

@@

[ ] LHT Bartomeus PNAS + Scheper PNAS + Traitbase (Var) Nacho
[X] Brain: MA (Spain + ND + US Ferran + US Parker): MA
[ ] Habitats USA: MA; Others ¿?: MA
[ ] Exotic use ¿? (Nacho)
[ ] Innovation (some in MA bbdd)
[ ] Invasive species in US. (Nacho)
